---
name: Cory
surname: Waters
position: "Data Analyst"
address: "West Palm Beach, Florida"
phone: +561-329-8664
www: www.corywaters.com
email: "corywaters@gmail.com"
github: cswaters
linkedin: cory-waters-103421179
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tibble)

# Load Files
work_history <- readr::read_csv('../data/history.csv')
schools <- readr::read_csv('../data/education.csv')
awards <- readr::read_csv('../data/awards.csv')
skills <- readr::read_csv('../data/skills.csv')
```

# Professional Summary

Data Scientist/Analyst with 15 years of industry experience applying data science methods to real-world business problems. An analytical and pragmatic thinker with solid statistical skills, I have the ability to extract useful signals from noisey business data. I'm adept at turning those insights into actionable advice that create business value.

# Work History

```{r}
work_history %>%
  detailed_entries(
    what = pos,
    with = company,
    when = period,
    why = desc,
    where = where
  )
```

# Education 

```{r}
schools %>% 
  brief_entries(
    what=type,
    when=year,
    with=school
  )
```

# Awards

```{r}
awards %>% 
  brief_entries(
    what=award,
    when=year,
    with=with
  )
```


# Skills

```{r}

tibble(
  skills = c(
    'R, Python, SQL, Machine Learning, Excel, Risk Management, A/B Testing, Data Visualization, Data Analysis'
  )
) %>%
  brief_entries(what = skills,)


```


